---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# createdictionary

<!-- badges: start -->
<!-- badges: end -->

```{r}
# output: github_document
#   always_allow_html: true
```


This package of createdictionary was developed at the Neuroepidemiology Section (NES) of Laboratory of Epidemiology & Population Science (LEPS), NIA. The goal is to build a one-document dictionary from multiple datasets; the key values are extracted for each variable.  

## Installation

You can install the released version of createdictionary from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("createdictionary")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("LEPSNES/createdictionary")
```
## Example

This is a basic example which shows you how to solve a common problem:

```{r load libaries, include=FALSE}
library(createdictionary)
library(haven)
```


```{r example1}
## get folder path
df <- system.file(package = "haven")
## search all the files under the folder for sas dataset
dse <- flat2file(df, "*.sas7bdat")
## dic_value_extract_one_dataset_path uses file path as input
dse %>%
  dic_value_extract_one_dataset_path()

## dic_value_extract_one_dataset uses a data frame as input
dse[1] %>% 
  read_sas() %>% 
  dic_value_extract_one_dataset()

## dic_value_extract_one_var process a variable each time
dse %>% 
  read_sas() %>% 
  imap_dfr( ~ dic_value_extract_one_var(.x, .y))

```


```{r example2}
df <- "/LSC/NES/study/CARDIA/core datasets/Y25/DATA"
## on windows, use this
## df <- "T:/LEPS/NES/study/CARDIA/core datasets/Y25/DATA"
dse <- flat2file(df, "*.sas7bdat")
dse[3] %>%
  dic_value_extract_one_dataset_path()

dse[1:3] %>%
  map_dfr(dic_value_extract_one_dataset_path) %>% 
  slice_head(n=7)

```


Please check the help document for each function to see how to use them. 

``` r
?flat2file
?dic_value_extract_one_dataset_path
?dic_value_extract_one_dataset
?dic_value_extract_one_var

```



